Refinements for open automata

### 2023-03-03 2021-Refinement/paper/refinementarticleV2.tex
congruence in progress

@@

 \TODO{I will continue...}

@@

Thus we have, as $R$ contains the reachability of state $S_{12}$:\TODO{faire une jolie equation}
\begin{multline*}
V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
\implies \reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) \\
\implies
\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
\end{multline*}
\qed

>>>>

For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$ and $g_{13x}  \Leftrightarrow g^2_1$ and the actions of $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} = = \alpha^2_1$ and the actions of the holes in $J_{13}$ coincide by the composition.

The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.

@@

@@

Thus we have, as $R$ contains the reachability of state $s_{12}$:\TODO{faire une jolie equation}
\begin{multline*}
V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
\implies \reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) \\
\implies
\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
\end{multline*}
\qed
